R Notebook

### 2018-04-03 analysis/final_analysis.Rmd
Bootstrap feature analyses; add test mouse-tracking analysis

@@

# nonNativeSpeakerIDs <- unique((tangramSubjInfo %>% filter(nativeEnglish != "yes"))$gameid)
incompleteIDs <- unique((d_raw %>% group_by(gameid) %>% 
                           filter(length(unique(trialNum)) != 24))$gameid)
confused <- unique((subjInfo %>% filter(understandsInstructions != 'yes'))$gameid)

@@

d %>%
  group_by(context, hidden) %>%
  summarize(m = mean(numRawWords), se = sd(numRawWords)/sqrt(length(numRawWords))) %>%
  ggplot(aes(x = context, y = m, fill = hidden)) +
    geom_bar(stat = 'identity', position = dodge) +
    geom_errorbar(aes(ymin = m - se, ymax = m + se), position = dodge, width = 0.1) +
    theme_few() +
    ylab('mean # words') +
    theme(aspect.ratio = .5)

ggsave('~/Downloads/aggregated_means.pdf')
```

@@

>>>>

```{r}
subjInfo <- read_csv('../data/final/experiment2/planned_sample/turk/subjInfo.csv')
```

@@

# nonNativeSpeakerIDs <- unique((tangramSubjInfo %>% filter(nativeEnglish != "yes"))$gameid)
incompleteIDs <- unique((d_annotated %>% group_by(gameid) %>% 
                           filter(length(unique(trialNum)) != 24))$gameid)
confused <- unique((subjInfo %>% filter(understandsInstructions != 'yes'))$gameid)

@@

d %>%
  group_by(context, hidden) %>%
  tidyboot_mean(column = numRawWords) %>%
  ggplot(aes(x = context, y = empirical_stat, fill = hidden)) +
    geom_bar(stat = 'identity', position = dodge) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), position = dodge, width = 0) +
    theme_few() +
    ylab('mean # words') +
    theme(aspect.ratio = .5) +
    scale_fill_colorblind()

ggsave('~/Downloads/aggregated_means.pdf', width = 4, height = 2)
```

@@

```{r}
d.booted <- d %>% 
  gather(feature, mentioned, shapeMention, colorMention, textureMention) %>%
  group_by(context, hidden, feature) %>% 
  tidyboot_mean(column = mentioned)

ggplot(d.booted, aes(x = context, y = empirical_stat, fill = hidden)) + 
  geom_bar(stat = 'identity', position = dodge) +
  geom_errorbar(aes(ymax = ci_upper, ymin = ci_lower), position = dodge, width = 0) +
  facet_wrap(~ feature) + 
  theme_few() +
  theme(aspect.ratio = 1) + 
  ylab('% utterances with feature') +
  scale_fill_colorblind()

ggsave('~/Downloads/by-feature-analysis.pdf')
```

## Mouse-tracking

should be really straightforward but might help catch a bug for Exp. 1?

```{r}
d.mouse <- read_tsv('../data/final/experiment2/planned_sample/updateMouse/mouse.csv') %>%
  filter(!(gameid %in% badGames)) %>%
  left_join(d_annotated)

d.mouse %>%
  filter(distractorDistance != 'none') %>%
  mutate(distractorDistance = as.numeric(distractorDistance)) %>%
  group_by(gameid, trialNum) %>%
  mutate(initTime = first(localTime)) %>%
  group_by(context, hidden, gameid, trialNum, targetDistance < 300, distractorDistance < 300)  %>%
  summarize(firstTarget = first(localTime) - mean(initTime))
  # filter(distractorDistance < 300)
#  group_by()
```
